Total_SC

### 2020-05-31 doc/totalSC.Rmd
extra updates for total SC

load(file="~./MLH1repo/data/MLH1/MLH1_data_setup_5.12.20.RData")
#load(file="C:/Users/alpeterson7/Documents/MLH1repo/data/MLH1/MLH1_data_setup_12.20.19.RData")#most recent

@@

Total.SC_DF = read.xlsx2("~./MLH1repo/data/Total.SC_merge.MLH1.xlsx", header=TRUE, 1)

#this most recent version -- is missing most measures for MOLF_m
```

@@

@@

#check for duplicatations of the random name
original_DF$Random.Name <- as.character(original_DF$Random.Name)
duplies <- original_DF[duplicated(original_DF$Random.Name),]
#3 duplicate rows in original DF -- because Random name was blank -- how will these be matched to total.SC?

@@

@@

#this is a nice merged excel file, still has X, and might have some 'outlier' images
Total.SC_DF.og <- Total.SC_DF
#quality is mess up here

@@

#Total.SC_DF <- Total.SC_DF %>% filter(X != "X")
#remvove Xs
Total.SC_DF <- Total.SC_DF[ !grepl("X", Total.SC_DF$X) , ]
#Total.SC_DF$X <- droplevels(Total.SC_DF$X)

@@

#table(Total.SC_DF$quality)

@@

this.plot_WSB.female <- ggplot(DF.2[DF.2$category == "WSB female",], aes(n.SC.pacc.bivs)) + geom_histogram(bins = 40)+ facet_wrap(~mouse)+ggtitle("Number of curated bivs per image")

@@

# -- EXAMINE the ggplot scatter plots for outliers
#tot.sc <- ggplot(data= MLH1.merge.Skel, aes(y = bin_size, x=strain))+ #geom_jitter()+facet_wrap(~category, scales = "free")

#round 1
SC.skel.outliers_round1 <- c(
  #MLH1.merge.Skel  %>% filter(category == "WSB male") %>% filter(skel_size > 2000)
  "10apr15_31mar15_WSB_m3_sp1_4_rev.tif",

  #MLH1.merge.Skel  %>% filter(category == "WSB female") %>% filter(skel_size > 2700)       
            "17nov16_3nov15_WSB_f1_sp3_4_rev.tif","1may16_3nov15_WSB_f1_sp2_6_rev.tif",

@@

MLH1.merge.Skel <- MLH1.merge.Skel[!MLH1.merge.Skel$fileName %in% SC.skel.outliers_round1, ]#62 removed

remove.mice_round2 <- c(
    #MLH1.merge.Skel  %>% filter(category == "G male") %>% filter(skel_size > 2500)
    "28jul15_22jun15_G_m2_sp1_5_rev.tif","12may15_30sep14_G_m5_sp1_26_rev.tif",

@@

#MLH1.merge.Skel_2  %>% filter(category == "PWD male") %>% filter(skel_size > 2100)
"20jul15_18may15_PWD_m1_sp1_10_rev.tif","22mar15_10mar15_PWD_m2_sp1_11.2_rev.tif","22mar15_10mar15_PWD_m1_sp1_4.1_rev.tif","20jul15_18may15_PWD_m1_sp1_7.2_rev.tif",

@@

#MLH1.merge.Skel_2  %>% filter(category == "SPRET male") %>% filter(skel_size < 1900 ) 
 "24may17_8may17_SPRET_m1_sp1_21.1_rev.tif",
#SPRET female X
#MLH1.merge.Skel_2  %>% filter(category == "HMI male") %>% filter(skel_size < 1000 ) 
"29dec17_4dec17_HMI_m1_sp1_4.1_rev.tif"
)
#3remove.mice_round2

MLH1.merge.Skel <- MLH1.merge.Skel[!MLH1.merge.Skel$fileName %in% remove.mice_round2, ]

@@

`r sum( length(SC.skel.outliers_round1), length(remove.mice_round2) )` images were removed as probable outliers.  ~20 outliers were removed from total.sc.skel.

@@

#Below threshold is are the values to use
write.xlsx2(Total.SC_DF, "Total.SC_DF.xlsx", sheetName = "Sheet1", 
            col.names = TRUE, row.names = FALSE, append = FALSE)

>>>>

load(file="~./MLH1repo/data/MLH1/MLH1_data_setup_5.30.20.RData")
#load(file="~./MLH1repo/data/MLH1/MLH1_data_setup_5.12.20.RData")
#load(file="C:/Users/alpeterson7/Documents/MLH1repo/data/MLH1/MLH1_data_setup_12.20.19.RData")#most recent

@@

#remake THIS FILE IT IS MISSING BATCHES 16 and 15
Total.SC_DF = read.xlsx2("~./MLH1repo/data/Total.SC_DF_2.20.xlsx", header=TRUE, 1)

#Total.SC_DF.2.20 = read.csv("~./MLH1repo/data/SCskel_output_feb20.csv", header = TRUE, strip.white = TRUE)
#this most recent version -- is missing most measures for MOLF_m
```

@@

#Total.SC_DF.og <- Total.SC_DF.2.20
SC.skel <- Total.SC_DF.2.20

@@

#check for duplicatations of the random name
original_DF$Random.Name <- as.character(original_DF$Random.Name)
duplies <- original_DF[duplicated(original_DF$Random.Name),]
#3 duplicate rows in original DF -- because Random name was blank -- how will these be matched to total.SC?
```

@@

#write the new SC excel file
#write.xlsx2(MLH1.merge.Skel, "Total.SC_DF_2.20.xlsx", sheetName = "Sheet1", 
#            col.names = TRUE, row.names = FALSE, append = FALSE)
```

@@

#total SC_DF is the new file, dataframe
#this is a nice merged excel file, still has X, and might have some 'outlier' images
Total.SC_DF.og <- Total.SC_DF
Total.SC_DF <- Total.SC_DF
#quality is mess up here

@@

#Total.SC_DF <- Total.SC_DF %>% filter(X != "X")
#remvove Xs
Total.SC_DF <- Total.SC_DF[ !grepl("X", Total.SC_DF$X) , ]
Total.SC_DF <- Total.SC_DF[ !grepl("x", Total.SC_DF$X) , ]
#Total.SC_DF$X <- droplevels(Total.SC_DF$X)

@@

str(Total.SC_DF)
```

@@

this.plot_WSB.female <- ggplot(DF.2[DF.2$category == "WSB female",], aes(n.SC.pacc.bivs)) + geom_histogram(bins = 40)+ facet_wrap(~mouse)+ggtitle("Number of curated bivs per image")
```

@@

#EXAMINE the ggplot scatter plots for outliers
tot.sc.ggplot <- ggplot(data= (Total.SC_DF %>% filter(category == "CAST male")  ),
                        aes(y = bin_size, x=mouse))+ geom_jitter()+facet_wrap(~category, scales = "free")

#MOLF male bin_size skel_size
#noe there's a molf female

#need round 3 for the batch 16 15
SC.skel.outliers_round3 <- c("9sep16_30jun16_CAST_m1_sp1_13_rev.tif",
  "1may16_3nov15_WSB_f1_sp2_1_rev.tif", "30jul15_12jun15_WSB_m2_sp1_1_rev.tif",                            "6mar18_1feb18_LEW_m1_sp1_18_rev.tif", "2jul17_20dec16_LEW_m2_sp1_8_rev.tif", "9jun18_8may17_LEW_m1_sp1_16_rev.tif",
  "12jan17_4jan17_LEW_f3_sp1_1_rev.tif","9apr18_1feb18_LEW_f1_sp1_7_rev.tif",      "13jan15_30sep14_G_m1_sp1_8_rev.tif", "28jul15_22jun15_G_m2_sp1_7.2_rev.tif", "1oct16_1apr16_G_m4_sp1_5_rev.tif", "27jul15_22jun15_G_m2_sp1_6_rev.tif",        "22jun18_24aug17_PERC_m1_sp1_11_rev.tif",
  "8apr15_24mar15_PWD_m2_sp1_4_rev.tif", "11mar15_28feb15_PWD_f1_sp1_13_rev.tif",  "8jun15_23apr15_PWD_f2_sp1_21_rev.tif", "11mar15_28feb15_PWD_f6_sp1_4_rev.tif",
  "5apr18_11jan18_KAZ_f2_sp1_17_rev.tif",
  "6aug19_10jul19_KAZ_m3_sp1_8.3_rev.tif",  "6aug19_10jul19_KAZ_m2_sp1_5.3_rev.tif", "6aug19_10jul19_KAZ_m3_sp1_5.2_rev.tif  6aug19_10jul19_KAZ_m3_sp1_9_rev.tif",  "6aug19_10jul19_KAZ_m2_sp1_1.2_rev.tif","6aug19_10jul19_KAZ_m2_sp1_4.1_rev.tif", "6aug19_10jul19_KAZ_m1_sp1_11.3_rev.tif", "6aug19_10jul19_KAZ_m1_sp1_11.1_rev.tif", "6aug19_10jul19_KAZ_m1_sp1_11.6_rev.tif", "27jul19_26oct18_SKIVE_f1_sp1_2_rev.tif", "18jul19_31may19_SKIVE_m2_sp1_22.2_rev.tif", "4jul18_8jun18_CZECH_m1_sp1_17.1_rev.tif", "29nov16_13nov16_MSM_f1_sp1_10_rev.tif", "28jul17_30may17_SPRET_m1_sp1_3_rev.tif","24may17_8may17_SPRET_m1_sp1_14_rev.tif", "26sep18_19may18_SPIC_m2_sp1_18_rev.tif", "26sep18_19may18_SPIC_m2_sp1_20_rev.tif", "6jun19_28jun18_SPIC_m2_sp1_8.1_rev.tif", "29dec17_4dec17_SPIC_f2_sp1_11_rev.tif", "29dec17_4dec17_SPIC_f2_sp1_3_rev.tif")

# ( Total.SC_DF  %>% filter(category == "SPIC male") %>% filter(bin_size > 32000) )$fileName

#KAZ -- has lower outliers?!
#MSM also has kinda strange pattern

Total.SC_DF <- Total.SC_DF[!Total.SC_DF$fileName %in% SC.skel.outliers_round3, ]

#round 1
SC.skel.outliers_round1 <- c(

  "10apr15_31mar15_WSB_m3_sp1_4_rev.tif", "1jul15_12jun15_WSB_f2_sp1_1_rev.tif",

            "17nov16_3nov15_WSB_f1_sp3_4_rev.tif","1may16_3nov15_WSB_f1_sp2_6_rev.tif",

@@

Total.SC_DF <- Total.SC_DF[!Total.SC_DF$fileName %in% SC.skel.outliers_round1, ]#62 removed

remove.mice_round2 <- c(
    #MLH1.merge.Skel  %>% filter(category == "G male") %>% filter(skel_size > 2500)

  #Total.SC_DF %>% filter(category == "WSB male") %>% filter(bin_size > 25000) )$fileName
    " 30jul15_12jun15_WSB_m2_sp1_1_rev.tif", "10apr15_31mar15_WSB_m3_sp1_11_rev.tif", "10apr15_31mar15_WSB_m3_sp1_3.1_rev.tif", "2mar15_30dec14_WSB_m4_sp3_32_rev.tif", "10apr15_31mar15_WSB_m3_sp1_4_rev.tif", "28jul15_22jun15_G_m2_sp1_5_rev.tif","12may15_30sep14_G_m5_sp1_26_rev.tif",

@@

#MLH1.merge.Skel_2  %>% filter(category == "PWD male") %>% filter(skel_size > 2100)
"20jul15_18may15_PWD_m1_sp1_10_rev.tif","22mar15_10mar15_PWD_m2_sp1_11.2_rev.tif","22mar15_10mar15_PWD_m1_sp1_4.1_rev.tif","20jul15_18may15_PWD_m1_sp1_7.2_rev.tif",  "6mar15_1mar15_PWD_m1_sp4_1_rev.tif",

@@

#MLH1.merge.Skel_2  %>% filter(category == "SPRET male") %>% filter(skel_size < 1900 ) 
 "24may17_8may17_SPRET_m1_sp1_21.1_rev.tif",
#SPRET female X
#MLH1.merge.Skel_2  %>% filter(category == "HMI male") %>% filter(skel_size < 1000 ) 
"29dec17_4dec17_HMI_m1_sp1_4.1_rev.tif"
)

Total.SC_DF <- Total.SC_DF[!Total.SC_DF$fileName %in% remove.mice_round2, ]

@@

`r sum( length(SC.skel.outliers_round1), length(remove.mice_round2), length(SC.skel.outliers_round3) )` images were removed as probable outliers.  ~20 outliers were removed from total.sc.skel.

@@

#Below threshold is are the values to use
write.xlsx2(Total.SC_DF, "Total.SC_DF_5.31.20.xlsx", sheetName = "Sheet1", 
            col.names = TRUE, row.names = FALSE, append = FALSE)
